Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 conclusion.tex
fixing error.

Thanks to the efforts captured in this paper, the time-averaged utilization of
Titan has consistently been upwards of 90\%. Compare this to the time averaged
utilization of other similar leadership machines such as NSF's flagship Blue
Waters, where the average utilization fluctuates between 60-80\% (XDMoD)
machine~\cite{bw-sucks}. These
% impressive if not
unprecedented efficiency gains aside, this work is just a starting point towards
more effective operational models for future leadership and online analytical
platforms~\cite{foap-url}. These platforms will have to support ever increasing
complex workloads with varying models for dynamic resource federation. Recent
efforts with Google Cloud for the CMS experiment --
HEPCloud~\cite{hepcloud,google- hep} represent similar yet different approaches
to dynamic resource federation.

>>>>

Thanks to the efforts captured in this paper, the time-averaged utilization of
Titan has consistently been upwards of 90\%. Compare this to the time averaged
utilization of other similar leadership machines such as NSF's flagship Blue
Waters, where the average utilization fluctuates between 60-80\% (XDMoD)
machine~\cite{bw-sucks}. These
% impressive if not
unprecedented efficiency gains aside, this work is just a starting point towards
more effective operational models for future leadership and online analytical
platforms~\cite{foap-url}. These platforms will have to support ever increasing
complex workloads with varying models for dynamic resource federation. Recent
efforts with Google Cloud for the CMS experiment --
HEPCloud~\cite{hepcloud,googlehep} represent similar yet different approaches
to dynamic resource federation.
